Interactive Summarization of Relational Tables

### 2014-11-15 TableSummarization/Paper/intro.tex
small change to intro

\section{Introduction}

Drill down (and roll up)~\cite{export:69578} are very useful tools for exploring
relational tables.
In this paper we study an extension of drill down
that lets users zoom into the more ``interesting'' parts of a table,
with fewer operations and without having to examine as much data
as traditional drill down.
We call our approach {\em smart drill down};
it does not replace traditional drill down but we will argue is a very
useful complement.
The best way to explain smart drill down is through a simple example.

>>>>

\section{Introduction}
Analysts often use OLAP (Online Analytical Processing) operations
such as drill-down (and roll-up)~\cite{export:69578} to explore
relational databases. 
These operations are very useful for analytics and data exploration and have stood the test of time;
all commercial database systems in existence support these operations.

However, there are cases where drill-down is ineffective; 
for example, when the number of distinct values
in a column is large, vanilla drill-down 
could easily overwhelm analysts by presenting them with too many 
results (i.e., aggregates). 
Further, drill-down only allows us to instantiate values
in one column at a time, instead of allowing simultaneous drill-downs
on multiple columns---simultaneous drill-down on multiple columns 
could once again suffer from the problem
of having too many results, stemming from distinct combinations of column values.

In this paper, we present a new interaction operator 
that is an extension to a traditional 
drill-down operator, aimed at providing {\em complementary}
functionality to drill-down in cases where drill-down is
ineffective. We call our operator {\em smart drill-down}.
At a high level, smart drill-down lets analysts zoom into
the more ``interesting'' parts of a table or a database,
with fewer operations, and without having to examine as much
data as traditional drill-down.
Note that our goal is to {\em not} replace traditional 
drill-down functionality, which we believe is essential;
instead, our goal is to provide auxiliary functionality 
which the analyst is free to use whenever they find 
traditional drill-downs ineffective.

In addition to presenting this new operator called smart drill-down, in this paper, 
we also present techniques to compute the results for this
operator {\em in an interactive fashion} on increasingly larger databases. 
Unlike the traditional OLAP setting, these computations 
require no pre-materialization, and can be implemented 
within any relational database system with no additional storage.

% Drill down (and roll up)~\cite{export:69578} are very useful tools for exploring
% relational tables.
% In this paper we study an extension of drill down
% that lets users zoom into the more ``interesting'' parts of a table,
% with fewer operations and without having to examine as much data
% as traditional drill down.
% We call our approach {\em smart drill down};
% it does not replace traditional drill down but we will argue is a very
% useful complement.
The best way to explain smart drill down is through a simple example.
